The Weakly Nonlinear Saturation of the Magnetorotational Instability

### 2014-09-12 paper/mri_paper.tex
bib stuff

This work builds on the weakly nonlinear analysis of \citeauthor{Umurhan:2007hs} (\citeyear{Umurhan:2007hs}).

@@

\bibitem[{Umurhan et al.(2007)}]{Umurhan:2007hs}
Umurhan, O M, Regev, O, Menou, K, Phys. Rev. E, 76, 036310

>>>>

This work builds on the investigations of \citeauthor{Umurhan:2007hs} (\citeyear{Umurhan:2007hs}; see also \citei{Umurhan:2007dz}), who first conducted an analytic analysis of the MRI in the weakly nonlinear regime.

@@

\bibitem[{Umurhan et al.(2007b)}]{Umurhan:2007hs}
Umurhan, O M, Regev, O, Menou, K, Phys. Rev. E, 76, 036310

\bibitem[{Umurhan et al.(2007a)}]{Umurhan:2007dz}
Umurhan, O M, Regev, O, Menou, K, Phys. Rev. Letters, 98, 034501
